---
title: "Statistical Analysis of Coworking Space"
author: "Taylor Hughes"
date: "4/20/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(caTools)
library(dplyr)
```

# Statistical Analyses
First we will run a comparison on 3 sets of data - 

* Proportions of each statistic for Coworking Members
* Proportions of each statistic for Non-Coworking Training data
* Proportions of each statistic for Market Area Data

The outcome of this will allow us to make a hypothesis on:

* Statistics that will have a strong impact on the model
* Which statistical factors would make our Market Area prove to be a weak market for potential customers
* Which statistical factors would make our Market Area prove to be a strong market for potential customers

## Distance to Home
```{r}
TrainCensus2 <- read.table("TrainCensus2", header = TRUE)
Census <- read.table("Census", header = TRUE)
MarketCensus <- read.table("MarketCensus", header = TRUE)

table(TrainCensus2$CommuteTime, useNA = "ifany")
table(Census$CommuteTime, useNA = "ifany")
table(MarketCensus$CommuteTime, useNA = "ifany")


DTHTrain <- ggplot(TrainCensus2, aes(x="")) + 
  geom_bar(aes(fill=CommuteTime), position = "fill") + 
  ggtitle("Coworking Members")
DTHTrain

DTHCensus <- ggplot(Census, aes(x=factor(0))) + 
  geom_bar(aes(fill=CommuteTime), position = "fill") +
  ggtitle("Non-Coworking Members")
DTHCensus

DTHMarket <- ggplot(MarketCensus, aes(x=factor(0))) + 
  geom_bar(aes(fill=CommuteTime), position = "fill") +
  ggtitle("Market Area")
DTHMarket
```

## Mode of Transportation
```{r}
table(TrainCensus2$TransportationMode, useNA = "ifany")
table(Census$TransportationMode, useNA = "ifany")
table(MarketCensus$TransportationMode, useNA = "ifany")


MOTTrain <- ggplot(TrainCensus2, aes(x=factor(0))) + 
  geom_bar(aes(fill=TransportationMode), position = "fill") + 
  ggtitle("Coworking Members")
MOTTrain

MOTCensus <- ggplot(subset(Census, subset = !is.na(TransportationMode)), aes(x=factor(0))) + 
  geom_bar(aes(fill=TransportationMode), position = "fill") +
  ggtitle("Non-Coworking Members")
MOTCensus

MOTMarket <- ggplot(MarketCensus, aes(x=factor(0))) + 
  geom_bar(aes(fill=TransportationMode), position = "fill") +
  ggtitle("Market Area")
MOTMarket
```

## Age of Member
```{r}
table(TrainCensus2$AgeBracket, useNA = "ifany")
table(Census$AgeBracket, useNA = "ifany")
table(MarketCensus$AgeBracket, useNA = "ifany")


AOMTrain <- ggplot(TrainCensus2, aes(x=factor(0))) + 
  geom_bar(aes(fill=AgeBracket), position = "fill") + 
  ggtitle("Coworking Members")
AOMTrain

AOMCensus <- ggplot(subset(Census, subset = !is.na(AgeBracket)), aes(x=factor(0))) + 
  geom_bar(aes(fill=AgeBracket), position = "fill") +
  ggtitle("Non-Coworking Members")
AOMCensus

AOMMarket <- ggplot(MarketCensus, aes(x=factor(0))) + 
  geom_bar(aes(fill=AgeBracket), position = "fill") +
  ggtitle("Market Area")
AOMMarket
```

## Job Type
```{r}
table(TrainCensus2$ClassOfWorker, useNA = "ifany")
table(Census$ClassOfWorker, useNA = "ifany")
table(MarketCensus$ClassOfWorker, useNA = "ifany")


COWTrain <- ggplot(subset(TrainCensus2, subset = !is.na(ClassOfWorker)), aes(x=factor(0))) + 
  geom_bar(aes(fill=ClassOfWorker), position = "fill") + 
  ggtitle("Coworking Members")
COWTrain

COWCensus <- ggplot(subset(Census, subset = !is.na(ClassOfWorker)), aes(x=factor(0))) + 
  geom_bar(aes(fill=ClassOfWorker), position = "fill") +
  ggtitle("Non-Coworking Members")
COWCensus

COWMarket <- ggplot(subset(MarketCensus, subset = !is.na(ClassOfWorker)), aes(x=factor(0))) + 
  geom_bar(aes(fill=ClassOfWorker), position = "fill") +
  ggtitle("Market Area")
COWMarket
```

## Profession
```{r}
table(TrainCensus2$OccupationType, useNA = "ifany")
table(Census$OccupationType, useNA = "ifany")
table(MarketCensus$OccupationType, useNA = "ifany")


OTTrain <- ggplot(subset(TrainCensus2, subset = !is.na(OccupationType)), aes(x=factor(0))) + 
  geom_bar(aes(fill=OccupationType), position = "fill") + 
  ggtitle("Coworking Members")
OTTrain

OTCensus <- ggplot(subset(Census, subset = !is.na(OccupationType)), aes(x=factor(0))) + 
  geom_bar(aes(fill=OccupationType), position = "fill") +
  ggtitle("Non-Coworking Members")
OTCensus

OTMarket <- ggplot(subset(MarketCensus, subset = !is.na(OccupationType)), aes(x=factor(0))) + 
  geom_bar(aes(fill=OccupationType), position = "fill") +
  ggtitle("Market Area")
OTMarket
```

## Gender

```{r}
table(TrainCensus2$Sex, useNA = "ifany")
table(Census$Sex, useNA = "ifany")
table(MarketCensus$Sex, useNA = "ifany")


STrain <- ggplot(subset(TrainCensus2, subset = !is.na(Sex)), aes(x=factor(0))) + 
  geom_bar(aes(fill=Sex), position = "fill") + 
  ggtitle("Coworking Members")
STrain

SCensus <- ggplot(subset(Census, subset = !is.na(Sex)), aes(x=factor(0))) + 
  geom_bar(aes(fill=Sex), position = "fill") +
  ggtitle("Non-Coworking Members")
SCensus

SMarket <- ggplot(subset(MarketCensus, subset = !is.na(Sex)), aes(x=factor(0))) + 
  geom_bar(aes(fill=Sex), position = "fill") +
  ggtitle("Market Area")
SMarket
```

## Relationship Status
```{r}
table(TrainCensus2$MaritalStatus, useNA = "ifany")
table(Census$MaritalStatus, useNA = "ifany")
table(MarketCensus$MaritalStatus, useNA = "ifany")


MSTrain <- ggplot(subset(TrainCensus2, subset = !is.na(MaritalStatus)), aes(x=factor(0))) + 
  geom_bar(aes(fill=MaritalStatus), position = "fill") + 
  ggtitle("Coworking Members")
MSTrain

MSCensus <- ggplot(subset(Census, subset = !is.na(MaritalStatus)), aes(x=factor(0))) + 
  geom_bar(aes(fill=MaritalStatus), position = "fill") +
  ggtitle("Non-Coworking Members")
MSCensus

MSMarket <- ggplot(subset(MarketCensus, subset = !is.na(MaritalStatus)), aes(x=factor(0))) + 
  geom_bar(aes(fill=MaritalStatus), position = "fill") +
  ggtitle("Market Area")
MSMarket
```

## Health Insurance Status
```{r}
table(TrainCensus2$HealthInsurance, useNA = "ifany")
table(Census$HealthInsurance, useNA = "ifany")
table(MarketCensus$HealthInsurance, useNA = "ifany")


HITrain <- ggplot(subset(TrainCensus2, subset = !is.na(HealthInsurance)), aes(x=factor(0))) + 
  geom_bar(aes(fill=HealthInsurance), position = "fill") + 
  ggtitle("Coworking Members")
HITrain

HICensus <- ggplot(subset(Census, subset = !is.na(HealthInsurance)), aes(x=factor(0))) + 
  geom_bar(aes(fill=HealthInsurance), position = "fill") +
  ggtitle("Non-Coworking Members")
HICensus

HIMarket <- ggplot(subset(MarketCensus, subset = !is.na(HealthInsurance)), aes(x=factor(0))) + 
  geom_bar(aes(fill=HealthInsurance), position = "fill") +
  ggtitle("Market Area")
HIMarket
```

## Home Office
```{r}
table(TrainCensus2$HomeOffice, useNA = "ifany")
table(Census$HomeOffice, useNA = "ifany")
table(MarketCensus$HomeOffice, useNA = "ifany")


HOTrain <- ggplot(subset(TrainCensus2, subset = !is.na(HomeOffice)), aes(x=factor(0))) + 
  geom_bar(aes(fill=HomeOffice), position = "fill") + 
  ggtitle("Coworking Members")
HOTrain

HOCensus <- ggplot(subset(Census, subset = !is.na(HomeOffice)), aes(x=factor(0))) + 
  geom_bar(aes(fill=HomeOffice), position = "fill") +
  ggtitle("Non-Coworking Members")
HOCensus

HOMarket <- ggplot(subset(MarketCensus, subset = !is.na(HomeOffice)), aes(x=factor(0))) + 
  geom_bar(aes(fill=HomeOffice), position = "fill") +
  ggtitle("Market Area")
HOMarket
```

## Education
```{r}
table(TrainCensus2$EducationLevel, useNA = "ifany")
table(Census$EducationLevel, useNA = "ifany")
table(MarketCensus$EducationLevel, useNA = "ifany")


ELTrain <- ggplot(subset(TrainCensus2, subset = !is.na(EducationLevel)), aes(x=factor(0))) + 
  geom_bar(aes(fill=EducationLevel), position = "fill") + 
  ggtitle("Coworking Members")
ELTrain

ELCensus <- ggplot(subset(Census, subset = !is.na(EducationLevel)), aes(x=factor(0))) + 
  geom_bar(aes(fill=EducationLevel), position = "fill") +
  ggtitle("Non-Coworking Members")
ELCensus

ELMarket <- ggplot(subset(MarketCensus, subset = !is.na(EducationLevel)), aes(x=factor(0))) + 
  geom_bar(aes(fill=EducationLevel), position = "fill") +
  ggtitle("Market Area")
ELMarket
```

## Relative Income
```{r}
table(TrainCensus2$RelativeIncome, useNA = "ifany")
table(Census$RelativeIncome, useNA = "ifany")
table(MarketCensus$RelativeIncome, useNA = "ifany")


RITrain <- ggplot(subset(TrainCensus2, subset = !is.na(RelativeIncome)), aes(x=factor(0))) + 
  geom_bar(aes(fill=RelativeIncome), position = "fill") + 
  ggtitle("Coworking Members")
RITrain

RICensus <- ggplot(subset(Census, subset = !is.na(RelativeIncome)), aes(x=factor(0))) + 
  geom_bar(aes(fill=RelativeIncome), position = "fill") +
  ggtitle("Non-Coworking Members")
RICensus

RIMarket <- ggplot(subset(MarketCensus, subset = !is.na(RelativeIncome)), aes(x=factor(0))) + 
  geom_bar(aes(fill=RelativeIncome), position = "fill") +
  ggtitle("Market Area")
RIMarket
```

##Conclusions
Listed below are the observations we've made:

* Shockingly, Distance to Home does not play a large role in predicting Coworking Membership, since the 80% of the Coworking Survey and 80% of LA County all live within a 20 minute drive of their Coworking Space.
* Far more Coworkers walked and biked to the Coworking Space compared to the average non-Coworker in Los Angeles County. Only around 1% of people in LA bike, with around 3% walking. However, the same proportions of people took Public Transportation.
+ Even fewer people in my targeted market area walk and bike, so I will leave this statistic alone. Seems like this will have a slight negative effect on my Market population.
* There are more 18-29 year olds proportionally going to Coworking Spaces than exist in the LA County population. There are far more 30-39 year olds in the Coworking Spaces as well.
* There are vastly more Entrepreneurs, Freelancers, and Other in Coworking Spaces than in LA County.There are vastly less Employees proportionally in Coworking Spaces.
+ The proportion in the Market Area seems to be roughly the same as in LA.
* There are less Designers, IT workers, PR, Researchers, and Writers in LA County than in Coworking Spaces. There are vastly more "Other" folks in LA County than in Coworking Spaces.
* There are proportionally more men in Coworking Spaces than in LA County.
* There are roughly the same proportion of married people, but there are less Unmarried in LA County and more Separated/Divorced/Widowed.
* There are slightly more uninsured in Coworking Spaces.
* There are vastly more people in Coworking Spaces who were previously working in Home Offices than there are people working in Home Offices in LA County.
* There are vastly more people with Bachelors or Masters degrees as their highest educational attainment in Coworking Spaces than in LA County.
+ There are more people with Masters Degrees and PhDs within my Market Area, which will have a positive effect on the model.
* There are vastly more Somewhere in the Middle, Rather High, and Very High relative incomes in Coworking Spaces than in LA County.
+ The Market Area has more folks Somewhere in the Middle than LA County, which will skew the model positively in our favor.

## Skewing the Training Set
I will need to skew my data set in order to have a model that has more polar opposites between the non-Coworkers and the Coworkers. While this seems biased, it will exaggerate the scores in a more scalable and readable way. I will then compare my Market Area to an area which I know is a strong Coworking market area and one which is not a strong Coworking market area to see in order to eliminate the bias.

The general approach I will take is this: I will delete a random 50% sample from the non-Coworking data set of whichever categorical variable is the highest in the Coworking data. I will also delete 50% of all non-Coworking observations for which the Coworking categories will be statistically significant.

* I will delete 50% of "Yes" CommuteTime entries
* I will delete 50% of Drivers, Bikers, and Walkers from "TransportationMode"
* I will delete 50% of 18-39 year olds from "AgeBracket"
* I will delete 50% of Entrepreneurs, Freelancers, and Others. I will leave Employees the same since the non-Coworking set has a proportionally much larger proportion than the Coworking set.
* I will delete 50% of Designers, IT Workers, PR folks, Researchers, and Writers.
* I will delete 50% of men.
* I will delete 50% of Married and Unmarried people.
* I will delete 50% of the uninsured.
* I will delete 50% of people working out of Home Offices.
* I will delete 50% of Bachelors and Masters degrees.
* I will delete 50% of Somewhere in the Middle, Rather High, and Very High.

```{r}
Census2 <- Census

List <- split(Census, Census$CommuteTime)
List$Yes <- sample_frac(List$Yes, size = 0.5)
Census <- rbind(List$Yes, List$No)

Census$Random <- 0
Census$Random[Census$TransportationMode == "Driving" | Census$TransportationMode == "Biking" | Census$TransportationMode == "Walking"] <- 1
List <- split(Census, Census$Random)
List$"1" <- sample_frac(List$"1", size = 0.5)
Census <- rbind(List$"1", List$"0")

Census$Random <- 0
Census$Random[Census$AgeBracket == "18-29" | Census$AgeBracket == "30-39"] <- 1
List <- split(Census, Census$Random)
List$"1" <- sample_frac(List$"1", size = 0.5)
Census <- rbind(List$"1", List$"0")

Census$Random <- 0
Census$Random[Census$ClassOfWorker == "Freelancer" | Census$ClassOfWorker == "Entrepreneur" | Census$ClassOfWorker == "Other"] <- 1
List <- split(Census, Census$Random)
List$"1" <- sample_frac(List$"1", size = 0.5)
Census <- rbind(List$"1", List$"0")

Census$Random <- 0
Census$Random[Census$OccupationType == "Design" | Census$OccupationType == "IT" | Census$OccupationType == "PR, Marketing, Sales, Advertising" | Census$OccupationType == "Research" | Census$OccupationType == "Writing"] <- 1
List <- split(Census, Census$Random)
List$"1" <- sample_frac(List$"1", size = 0.5)
Census <- rbind(List$"1", List$"0")

Census$Random <- 0
Census$Random[Census$Sex == "Male"] <- 1
List <- split(Census, Census$Random)
List$"1" <- sample_frac(List$"1", size = 0.5)
Census <- rbind(List$"1", List$"0")

Census$Random <- 0
Census$Random[Census$MaritalStatus == "Married" | Census$MaritalStatus == "Not Married"] <- 1
List <- split(Census, Census$Random)
List$"1" <- sample_frac(List$"1", size = 0.5)
Census <- rbind(List$"1", List$"0")

Census$Random <- 0
Census$Random[Census$HealthInsurance == "No Health Insurance"] <- 1
List <- split(Census, Census$Random)
List$"1" <- sample_frac(List$"1", size = 0.5)
Census <- rbind(List$"1", List$"0")

Census$Random <- 0
Census$Random[Census$HomeOffice == "Not Home Office"] <- 1
List <- split(Census, Census$Random)
List$"1" <- sample_frac(List$"1", size = 0.5)
Census <- rbind(List$"1", List$"0")

Census$Random <- 0
Census$Random[Census$EducationLevel == "Bachelor" | Census$EducationLevel == "Master"] <- 1
List <- split(Census, Census$Random)
List$"1" <- sample_frac(List$"1", size = 0.5)
Census <- rbind(List$"1", List$"0")

Census$Random <- 0
Census$Random[Census$RelativeIncome == "Somewhere In The Middle" | Census$RelativeIncome == "Rather High" | Census$RelativeIncome == "Very High"] <- 1
List <- split(Census, Census$Random)
List$"1" <- sample_frac(List$"1", size = 0.5)
Census <- rbind(List$"1", List$"0")

Census <- subset(Census, select = -Random)
TrainCensus <- rbind(TrainCensus2, Census)
write.table(x = TrainCensus, file = "TrainCensus3")
write.table(x = Census2, file = "Census2")
```